Competing Constructions for German Measure Noun Phrases: from Usage Data to Experimental Validation

### 2017-04-05 Latex/article.tex
another claenup pass before finishing writing

In this section, I motivate the choice of statistical models which I use later in Section~\ref{sec:corpusstudies}.
Readers might think that the methods used here for modeling a grammatical alternation -- namely Hierarchical Regression and Generalised Linear Mixed Models (GLMMs) -- does not require much motivation.
After all, GLMMs have been established as the major tool in the analysis of alternation phenomena (\citealp{BresnanEa2007,BresnanHay2010,BresnanFord2010,DivjakArppe2013,Gries2015,NessetJanda2010}, to name just a few publications).
Over the past few years, however, modified or alternative methods have been proposed, and I want to make a few remarks on Bayesian estimation (see \citealp{GelmanEa2014}) as suggested in \cite{Levshina2016,Divjak2016a}.
Conceptually, I see three points of discussion that should be kept apart.
First, Bayesian methods are sometimes touted as superior tools for scientific inference compared to frequentist methods.
Second, it has been proposed that the Bayesian interpretation of probability is more cognitively adequate for the modeling of linguistic data.
Third, and very specific to this paper, given established methods in the modeling of alternation and variation, it has to be decided whether so-called Bayesian methods lead to substantially different results.

As for the first question, this is not quite the place to discuss it fully.
The basic distinction is a philosophical one and related to direct and inverse probability (\eg\ \citealp{Senn2011}).
Frequentists assume that models and parameters are fixed, for example a model specifiying that a coin is fair.
Given we know the distribution of the values measured, we can calculate for observed data (for example a measurement of $3$ heads in an experiment with $10$ tosses) how often such a result or a more extreme result would occur if the model were true and we repeated the experiment arbitrarily often.
This is essentially the frequentist notion of direct probability, \ie\ long-run frequencies under replication.
What makes this attractive is that a model -- specified with reference to a substantive theory of the given phenomenon -- can fail on given data, and if it does not, the outcome of the experiment contributes to the overall well-testedness of the theory.
Bayesian approaches, on the other hand, condition on the data and quantify (inductively) the probability of models given specific observations.
The models are thus not fixed, and the probability is usually equated with researchers' posterior beliefs about models.
There is actually a debate among Bayesians whether and how a notion of hypothesis testing is compatible (or even already contained) in the Bayesian approach.
In \citet[10]{GelmanShalizi2013}, the authors acknowledge this and state about the standard inductive interpretation of Bayesianism that \textit{most of this received view of Bayesian inference is wrong}, and they develop a Bayesian notion of p values (see also \citealp{Mayo2013}, for a frequentist reply; also \citealp{Senn2011} on different strands of Bayesianism and their stance on inductive vs.\ deductive reasoning).
Clearly, in such quarrels between and among camps of philosophers of science and statisticians it is virtually impossible for mere practitioners to take sides.

These quarrels relate to the second question, however.
\citet[301--302]{Divjak2016a} speaks favourably of Bayesian methods because the Bayesian concept of probability is more adequate for cognitive modeling compared to the frequentist one.
Her argument is part of a larger body of literature asking for cognitively plausible modeling techniques, for example Naive Discriminative Learning (NDL; \citealp{Baayen2011,BaayenEa2013,MilinEa2016,TheijssenEa2013}).
Frequentist methods were, however, never designed as cognitive models (see above).
The actual question that emerges here is how we interpret our statistical models (estimated on corpus data).
Are they inductive models of cognitive representations that learners would infer from being exposed to the corpus data?%
\footnote{In which case we are doing \textit{data science in language research} in the words of \citealp{MilinEa2016}.}
Or are they tests of theories that are pre-specified and merely tested for predictive accuracy on linguistic output data contained in corpora.
In the former case, we should definitely resort to methods like NDL, which most likely would entail tossing most previous work done in (cognitive) linguistics into the bin and abandoning all high-level generalisations that most existing studies have been based upon.
In fact, arguments to this extreme effect and against using high-level generalisation have been made, for example in \cite{BaayenEa2016}, \citet[299--300]{Divjak2016a}, \cite{RamscarPort2016}, \cite{TheijssenEa2013}.
In the latter case, the cognitive commitment does not necessarily extend to the statistical methods used.
These methods then do not need to be any more cognitively plausible than an ANOVA used to analyse the results from an experiment.
I view my own work in the tradition of testing theories (embracing high-level generalisations) on data (see Sections~\ref{sec:germanmeasurenps}--\ref{sec:externalvalidation}), but I am fundamentally agnostic with respect to this question.
The best strategy for cognitive linguistics as a field might be to cultivate many methods while making sure that each method is applied carefully and competently.

The third point, then, is the most practically relevant in the context of this paper.
In her otherwise excellent study, \citet[251--252]{Levshina2016} argues for Bayesian estimation in mixed regression settings.
First, she claims that \textit{while frequentist statistics only allows one to test whether the null hypothesis can be rejected, Bayesian statistics enables one both to test the null hypothesis and to estimate the probability of specific parameter values given the data}.
This does not do justice to frequentist methods in that mere rejection of the null hypothesis is characteristic only of Fisher's approach, but in the Neyman-Pearson approach, results ideally \textit{favour} the main hypothesis (vs.\ the alternative), cf.\ \cite{Lehmann1993,Lehmann2011,Perezgonzalez2015}.
She then explains that a \textit{distinctive feature of Bayesian statistics is the use of so-called priors} and that \textit{posterior probabilities depend on both the prior beliefs and the data, whereas the results of a frequentist model depend only on the data} \cite[252]{Levshina2016}.
Remarkably, however, she does \textit{not} use informative priors, and in her footnote 8 \cite[252]{Levshina2016} admits that priors were probed using trial and error, such that the proclaimed advantage of Bayesian modeling was apparently not taken advantage of.%
\footnote{In the words of \cite{Senn2011}: \textit{You may believe you are a Bayesian but you are probably wrong}.
\cite[347--348]{GelmanHill2006} \textit{view any noninformative prior distribution as inherently provisional}.}
Now, Maximum Likelihood Estimation (MLE), the traditional method which could have been used here, is not exactly \textit{frequentist} in the sense of Neyman-Pearson testing theory.
MLE also conditions on the data in as much as it finds the most likely set of parameters given the data.
What is more, Bayesian estimators in fact incorporate the Likelihood function and merely multiply it by the prior \citep[PAGENUMBER??]{GelmanEa2014}.
If the prior is flat, results converge (see also \citealp[347]{GelmanHill2006}).
The same is true if the sample size is large compared to the number of parameters, at least for finite-dimensional models \citep[1119--1120]{Freedman1999}, a well-established result known as the Bernstein-von Mises theorem.%
\footnote{Relating back to cognitive plausibility, this means that Bayesian methods cannot be more cognitively plausible in these situations than Maximum Likelihood Estimation.}
With a modest model structure including $17$ fixed effects and $2,646$ data points in \cite{Levshina2016}, it is highly likely that the same results would have obtained with Maximum Likelihood methods.%
\footnote{In fact, she admits that changing the priors did not lead to substantially different results in her footnote 8.
  This is a clear sign that the prior is \textit{swamped by the data} (QUOTE??).}
If not, especially in case of convergence problems, this would have been an ideal occasion to demonstrate the superiority of Bayesian estimation.
After all, there are situations where Bayesian estimators can be more robust, namely with heavily censored data, complex hierarchical models, perfect separation, etc. (see \citealp{Freedman1999}, \citealp[345--348]{GelmanHill2006}).
I want to reiterate that these points do not in any way invalidate the study presented in \cite{Levshina2016}.
However, being \textit{Bayesian} is not among its selling points.
That said, I want to voice the concern that most likely many practitioners struggle with getting an adequate grasp of advanced statistical methods, and that it might therefore be wise to use the more conservative and better understood method if the alternative method is not absolutely required for substantive reasons.
In Section~\ref{sec:corpushierarchicalmodel}, I compare my own hierarchical models estimated with Bayesian and MLE estimators to demonstrate their expectable convergence.

@@

In this section, I introduce and illustrate the relevant alternating constructions.
I describe the narrowly defined syntactic configuration in which the alternation occurs, and I motivate the focus on \textit{only} this narrow (range rather than, for example, the whole range of nominal constructions expressing quantities).

I use the term \textit{measure noun phrase} (MNP) to refer a noun phrase (NP) in which a kind-denoting (count or mass) noun depends on another noun that specifies a quantity of the objects or the substance denoted by the kind noun.
I call the kind-denoting noun simply the \textit{kind noun} and the quantity-denoting noun the \textit{measure noun}.
Measure nouns can be all sorts of nouns which genuinely denote a quantity (such as \textit{litre} or \textit{amount}) but also nouns denoting containers, collections, etc. (such as \textit{glass} or \textit{bucket}).
In a similar vein, \citet[284]{Brems2003} considers nouns as measure nouns \textit{which, strictly speaking, do not designate a `measure', but display a more nebulous} (\textit{sic!}) \textit{potential for quantification} (see also \citealp[530]{Koptjevskaja2001}, and \citealp[338]{Rutkowski2007}).
For illustration purposes, in the English \textit{a cup of fine coffee}, \textit{cup} is the measure noun, and \textit{coffee} is the kind noun.

@@

\begin{exe}
  \ex\label{ex:intro:pseudopartitive}
  \begin{xlist}
    \ex[ ]{\label{ex:intro:pseudopartitive1}\gll Wir trinken [[eine Tasse]\Sub{Acc} [eines leckeren Kaffees]\Sub{Gen}]\Sub{Acc}.\\
    we drink a cup a tasty coffee\\
    \glt We drink a cup of a tasty coffee.}
    \ex[*]{\label{ex:intro:pseudopartitive2} Wir trinken [[eine Tasse]\Sub{Acc} [einen leckeren Kaffee]\Sub{Acc}]\Sub{Acc}.}
  \end{xlist}
\end{exe}

If the kind noun is bare -- \ie\ if it does neither come with a determiner nor a modifying adjective -- it has to agree in case with the measure noun, and the genitive seen in the PGC is not acceptable, see (\ref{ex:intro:narrowapposition}).

\begin{exe}
  \ex\label{ex:intro:narrowapposition}
  \begin{xlist}
    \ex[*]{\label{ex:intro:narrowapposition1} Wir trinken [[eine Tasse]\Sub{Acc} [Kaffees]\Sub{Gen}]\Sub{Acc}.}
    \ex[ ]{\label{ex:intro:narrowapposition2}\gll Wir trinken [[eine Tasse]\Sub{Acc} [Kaffee]\Sub{Acc}]\Sub{Acc}.\\
    we drink a cup coffee\\
    \glt We drink a cup of coffee.}
  \end{xlist}
\end{exe}

This construction is usually classified as a \textit{Narrow Apposition Construction} \citep{Loebel1986}, henceforth NAC.%
\footnote{The construction as in (\ref{ex:intro:narrowapposition2}) is also referred to as the \textit{Direct Partitive Construction} for other Germanic languages in which the PGC with the synthetic genitive is not available.
This nomenclature makes sense in contrast to the \textit{Indirect Partitive Construction} with prepositional linkers translating to `of' -- \ie\ analytic genitives -- in such languages, see \cite{HankamerMikkelsen2008} for Danish.
For German, this terminology is not distinctive enough, which is why I use the terms NAC and PGC.}
Notice that the unavailability of the genitive on the kind noun can be seen as following from a rather quirky constraint that genitive NPs in German require the presence of some strongly case-marked element (determiner or adjective) in addition to the head noun in order to be acceptable \citep{GallmannLindauer1994,Schachtl1989}.
While only an accusative is shown in (\ref{ex:intro:narrowapposition}), the kind noun obligatory agrees in case also with nominative and dative measure nouns.

@@

First of all, (\ref{it:intro:idiot}) refers to claims found in some grammars that a generic nominative, accusative, and even dative on the kind noun are used instead of the genitive (\PGCa) or case agreement (\NACa).
Overviews can be found in \citealp{Hentschel1993,Zimmer2015}.
It was shown empirically in \cite{Hentschel1993} that such variants are de facto not acceptable.
Also, in my corpus sample, they simply did not occur.
Even if they are accepted by some speakers, their extremely low frequency makes it virtually impossible to study them using either corpus methods (Section~\ref{sec:corpusstudies}) or experimental approaches (Section~\ref{sec:externalvalidation}), and I consequently ignore them.

@@

Turning to (\ref{it:intro:plurl}), readers might have noticed that so far only MNPs denoting quantities of substances (mass kind nouns such as \textit{ein Glas roter Wein\slash roten Weines} `a glass of red wine') have been discussed.
If the kind noun is a plural count noun as in \textit{ein Sack kleine Äpfel} (\NACa) or \textit{ein Sack kleiner Äpfel} (\PGCa) `a bag of small apples', a similar alternation between PGC and NAC can be observed.
In line with experimental results reported in \citet[15--16]{Zimmer2015}, I found that the PGC is so dominant with plural kind nouns (67 of 861 cases or over 92\%, cf.\ Section~\ref{sec:corpusstudies}) that the alternation cannot be analysed in the same way as in the singular case.%
\footnote{More concretely, I these cases were included in the regression analysis of the corpus data along with a factor encoding the number of the kind noun, this factor would most assuredly override any other regressor for the data points with a plural kind noun.}
While this will play a role in the interpretation of the corpus findings, MNPs with plural kind nouns will not be included in the corpus study and the experiments reported here.

@@

Second constructions with \textit{voll} (\textit{von})\slash\textit{voller} `full (of)' and \textit{mit} `with' are available, see (\ref{ex:alternatives}).

@@

My whole analysis is based on the idea that the syntactic structure [N\Sub{1}~[A~N\Sub{2}]\Sub{NP\Sub{2}}]\Sub{NP\Sub{1}} as instantiated in the \NACa\ and the \PGCa\ is ambiguous.
To show this, the first question is which noun constitutes the head of the whole construction.
This was answered quite clearly by \cite{Loebel1986} already (see also \citealp[213]{Eschenbach1994}, and \citealp[16]{GallmannLindauer1994}).
Subject-verb agreement is always realised on the measure noun, and we can therefore assume that the measure noun is the head.
However, the MNP-internal structure has more interesting cues to offer if the strong\slash weak inflection patterns of adjectives are taken into account.
In NPs with a strongly inflected determiner, attributive adjectives inflect according to the massively syncretistic \textit{weak} pattern.
%\footnote{The weak pattern has only two suffixes.
%The structural cases (nominative and accusative) in the singular are marked with \textit{-e}, the oblique cases (dative and genitive) as well as the entire plural are marked with \textit{-en}.
%The only exception to this rule is the masculine accusative singular, which is also marked with \textit{-en}.}
If there is no determiner (as is the case in the alternating constructions), attributive adjectives inflect like determiners themselves, however.
This is called the \textit{strong} inflectional pattern.
Thus, the adjectives in the \NACa\ and the \PGCa\ have properties of adjectives as well as determiners.
On the one hand, they are lexical adjectives and function as attributive modifiers.
On the other hand, they are inflected like determiners, and they are the leftmost element in the NP, which is typical of determiners.
This unusual double nature of adjectives in NPs without determiners leads to a plausible probabilistic interpretation of the pattern shown in Table~\ref{tab:constructions}.
Whenever speakers classify the adjective in the kind noun phrase more as a determiner, they have to use the \PGCa\ because, if there is a determiner, the PGC (just like in the case of the \PGCd) is the only option.
When they classify the adjective more as an adjective, the kind NP has no determiner, and they have to use the \NACa\ (like in the case of the \NACb).%
\footnote{While the generative analysis presented in \cite{Bhatt1990} cannot properly deal with probabilistic effects, Bhatt comes close to this interpretation by analysing the kind NP in the GPC as a DP and in the NAC as an NP.}

This morpho-syntactic ambiguity means that the \NACa\ is in fact a \NACb in disguise, and the \PGCa\ is a \PGCd in disguise.
This should ideally be reflected in the following basic selection effect:
It is known from frameworks like Collexeme Analysis \citep{GriesStefanowitsch2004} that lemmas are attracted with different strengths by competing constructions.
If the \NACa\ is highly similar to the \NACb\ and the \PGCa\ is highly similar to the \PGCd, the probability with which individual noun lemmas appear in the alternating constructions should be predictable at least partly from the relative frequency with which the same lemmas are used in the non-alternating constructions (see \citealp[246--249]{Levshina2016} for a similar idea in a different context).
Nouns which occur proportionally more often in the \PGCd\ should favour the \PGCa, and nouns which occur proportionally more often in the \NACb\ should favour the \NACa.
This basic attraction effect will be quantified in the corpus study Section~\ref{sec:corpusstudies}.

@@

Conversely, the NAC completely lacks this ability to form true partitives, and it forms a more restrictive environment with less combinatory and semantic flexibility.

@@

Furthermore, the grammaticalisation path as described above leads from NPs denoting individuated objects standing in a \textit{part-of} relation to a construction with a more diffuse \textit{quantity-of} relation.
Both types of relations can be numerically quantified -- in as much as a precise number of \textit{parts} or a numerically exact \textit{quantity} can be specified --, but it is much more prototypical of quantities to be specified with numerical precision.
Since the \NACa\ is more closely associated with the \textit{quantity-of} relation, cardinals as attributes of the measure noun are expected to have a higher proportional frequency in the \NACa.
For illustration, (\ref{ex:determiners}) shows the expected variants under this hypothesis.
In (\ref{ex:determiners:nac}), the measure noun is modified by a cardinal \textit{drei} `three', and hence the \NACa\ is preferred.
In (\ref{ex:determiners:pgc}), the measure noun is modified by a non-cardinal determiner \textit{einige} `some', and the \PGCa\ is preferred.

@@

The statistical models presented in Section~\ref{sec:corpusstudies} will be specified in a way that they could detect such a preference.

Finally, it has often been iterated that the \PGCa\ is more typical of higher registers or even exclusive to written language (see \citealp[320--323]{Hentschel1993}).
This is not surprising in as much as the genitive -- an intrinsic part of the PGC -- is generally underrepresented in colloquial vernacular variants of German as a result of a diachronic process wherein many (but not all) uses of the genitive are replaced by other cases or periphrastic constructions \citep{FleischerSchallert2011}.
Under an integral view of prototypes, which incorporate effects related to larger contexts and registers, such preferences can be to be part of the construction prototypes.
In the corpus study in Section~\ref{sec:corpusstudies}, register effects will therefore be modeled -- even if only using two very simple proxy variables.

>>>>

In this section, I motivate the choice of statistical models which I use later in Section~\ref{sec:corpusstudies}.
Readers might think that the method used here for modeling grammatical alternations -- namely Hierarchical Logistic Regression\slash Generalised Linear Mixed Models (GLMMs) -- does not require much motivation.
After all, GLMMs have been established as the major tool in the analysis of alternation phenomena (\citealp{BresnanEa2007,BresnanHay2010,BresnanFord2010,DivjakArppe2013,Gries2015,NessetJanda2010}, to name just a few publications).
Over the past few years, however, modified or alternative methods have been proposed.
From among these methods, I just make a few remarks on Bayesian estimation (see \citealp{GelmanEa2014}), as it was proposed in \cite{Levshina2016,Divjak2016a}.
Conceptually, I see three points of discussion that should be kept apart.
First, Bayesian methods are sometimes touted as superior tools for scientific inference compared to frequentist methods.
Second, it has been proposed that the Bayesian interpretation of probability is more cognitively adequate for the modeling of linguistic data.
Third, and very specific to this paper, given established methods in the modeling of alternation and variation, it has to be decided whether so-called Bayesian methods lead to substantially different results.

As for the first question, this is not quite the place to discuss it fully.
The basic distinction is a philosophical one and related to the concepts of \textit{direct} and \textit{inverse probability} (\eg\ \citealp{Senn2011}).
Frequentists assume that models and parameters are fixed, for example a model specifiying that a coin is fair.
We can then calculate for observed data (for example a measurement of $3$ heads in an experiment with $10$ tosses) how often such a result or a more extreme result would occur if the model were true and we repeated the experiment arbitrarily often.
This is essentially the frequentist notion of direct probability, \ie\ long-run frequencies under replication.
What makes frequentism attractive is that it lends itself to a theory of testing whether a theoretical prediction (a fixed model) was successful or not.
Such tests, if passed, contribute to the overall well-testedness of the theory.
Bayesian approaches, on the other hand, condition on the data and quantify inductively (in the standard interpretation) the probability of models given specific observations.
The models are thus not fixed, and the probability is usually equated with researchers' posterior beliefs about models or model parameters.
There is actually a debate among Bayesians whether and how a notion of hypothesis testing is compatible (or even already contained) in the Bayesian approach.
In \citet[10]{GelmanShalizi2013}, the authors -- prominent Bayesians -- acknowledge that theory testing is a desideratum, and they state about the standard inductive interpretation of Bayesianism that \textit{most of this received view of Bayesian inference is wrong}, and they develop a Bayesian notion of p values (see also \citealp{Mayo2013}, for a frequentist reply; also \citealp{Senn2011} on different strands of Bayesianism and their stance on inductive vs.\ deductive reasoning).
Clearly, in such quarrels between and among camps of philosophers of science and statisticians it is difficult for mere practitioners to take sides.

These quarrels relate to the second question, however.
\citet[301--302]{Divjak2016a} speaks favourably of Bayesian methods because the Bayesian concept of probability is more adequate for cognitive modeling compared to the frequentist one.
Her argument is part of a larger body of literature asking for cognitively plausible modeling techniques, for example Naive Discriminative Learning (NDL; \citealp{Baayen2011,BaayenEa2013,MilinEa2016,TheijssenEa2013}).
Frequentist methods were, however, never designed as cognitive models, but as systems of inference for researchers (see above).
The actual question that emerges here is how we interpret our statistical models (estimated on corpus data).
Are they inductive models of cognitive representations that learners would infer from being exposed to the corpus data?%
\footnote{In which case we are doing \textit{data science in language research} in the words of \citealp{MilinEa2016}.}
Or are they tests of theories that are pre-specified and merely tested for predictive accuracy on linguistic output data contained in corpora.
In the former case, we should definitely resort to methods like NDL.
However, this would most likely require us to toss most previous work done in (cognitive) linguistics into the bin and abandoning all high-level generalisations that most existing studies have been based upon.
In fact, arguments to this extreme effect and against using high-level generalisation have been made, for example in \cite{BaayenEa2016}, \citet[299--300]{Divjak2016a}, \cite{RamscarPort2016}, \cite{TheijssenEa2013}.
In the latter and less extreme case, the cognitive commitment does, however, not necessarily extend to the statistical methods used.
These methods then do not need to be any more cognitively plausible than an ANOVA used to analyse the results from an experiment.
I view my own work (see Sections~\ref{sec:germanmeasurenps}--\ref{sec:externalvalidation}) in the tradition of testing theories that embrace high-level generalisations in a probabilistic framework.
I remain fully agnostic with respect to the question which approach is `right'.
The best strategy for cognitive linguistics as a field might be to cultivate many methods while making sure that each method is applied carefully and competently.

The third point, then, is the most practically relevant in the context of this paper.
In her otherwise excellent study, \citet[251--252]{Levshina2016} argues for Bayesian estimation in mixed regression settings.
First, she claims that \textit{while frequentist statistics only allows one to test whether the null hypothesis can be rejected, Bayesian statistics enables one both to test the null hypothesis and to estimate the probability of specific parameter values given the data}.
This does not do justice to frequentist methods in that mere rejection of the null hypothesis is characteristic only of Fisher's approach, but in the Neyman-Pearson approach, results ideally \textit{favour} the main hypothesis vis-à-vis the alternative hypothesis (cf.\ \citealp{Lehmann1993,Lehmann2011,Perezgonzalez2015}).
She then explains that a \textit{distinctive feature of Bayesian statistics is the use of so-called priors} and that \textit{posterior probabilities depend on both the prior beliefs and the data, whereas the results of a frequentist model depend only on the data} \cite[252]{Levshina2016}.
Remarkably, however, she does \textit{not} use informative priors, and in her footnote 8 \cite[252]{Levshina2016} admits that priors were probed using trial and error, such that the proclaimed advantage of Bayesian modeling was apparently not taken advantage of.%
\footnote{In the words of \cite{Senn2011}: \textit{You may believe you are a Bayesian but you are probably wrong}.
\citet[347--348]{GelmanHill2006} \textit{view any noninformative prior distribution as inherently provisional} and give recommendations how to proceed once posteriors have been obtained from noninformative priors.}
Now, Maximum Likelihood Estimation (MLE) -- the traditional method which could have been used instead -- is not exactly \textit{frequentist} in the sense of Neyman-Pearson testing theory.
MLE also conditions on the data in as much as it finds the most likely set of parameters given the data.
What is more, Bayesian estimators in fact incorporate the Likelihood function and merely multiply it by the prior \citep[PAGENUMBER??]{GelmanEa2014}.
If the prior is flat, results converge (see also \citealp[347]{GelmanHill2006}).
The same is true if the sample size is large compared to the number of parameters, at least for finite-dimensional models \citep[1119--1120]{Freedman1999}, a well-established result known as the Bernstein-von Mises theorem.
With a modest model structure including $17$ fixed effects and $2,646$ data points in \cite{Levshina2016}, it is highly likely that the same results would have obtained with Maximum Likelihood methods.%
\footnote{In fact, she admits that changing the priors did not lead to substantially different results in her footnote 8.
  This is a clear sign that the prior is \textit{swamped by the data} (QUOTE??).
  Relating back to cognitive plausibility, this means that in the case at hand Bayesian methods cannot be more cognitively plausible than Maximum Likelihood Estimation.}
If not, especially in case of convergence problems, this would have been an ideal occasion to demonstrate the superiority of Bayesian estimation.
After all, there are situations where Bayesian estimators can be more robust, namely with heavily censored data, complex hierarchical models, perfect separation, etc. (see \citealp{Freedman1999}, \citealp[345--348]{GelmanHill2006}).
I want to reiterate that these points do not in any way invalidate the study presented in \cite{Levshina2016}.
However, being \textit{Bayesian} is not among its selling points.
That said, I want to voice the concern that most likely many practitioners are already struggling with getting an adequate grasp of advanced statistical methods, and that it might therefore be wise to use the more conservative and better understood method if the alternative method is not absolutely required for substantive reasons.
In Section~\ref{sec:corpushierarchicalmodel}, I compare my own hierarchical models estimated with Bayesian and MLE estimators to demonstrate their expectable convergence.

@@

In this section, I introduce and illustrate the relevant alternating constructions.
I describe the narrowly defined syntactic configuration in which the alternation occurs, and I motivate the focus on \textit{only} this narrow range (rather than, for example, the whole range of nominal constructions expressing quantities).

I use the term \textit{measure noun phrase} (MNP) to refer a noun phrase (NP) in which a kind-denoting (count or mass) noun depends on another noun that specifies a quantity of the objects or the substance denoted by the kind noun.
I call the kind-denoting noun simply the \textit{kind noun} and the quantity-denoting noun the \textit{measure noun}.
For illustration purposes, in the English \textit{a cup of fine coffee}, \textit{cup} is the measure noun, and \textit{coffee} is the kind noun.
Measure nouns can be all sorts of nouns which genuinely denote a quantity (such as \textit{litre} or \textit{amount}) but also nouns denoting containers, collections, etc. (such as \textit{glass} or \textit{bucket}).
In a similar vein, \citet[284]{Brems2003} considers nouns as measure nouns \textit{which, strictly speaking, do not designate a `measure', but display a more nebulous} (\textit{sic!}) \textit{potential for quantification} (see also \citealp[530]{Koptjevskaja2001}, and \citealp[338]{Rutkowski2007}).

@@

\begin{exe}
%  \ex\label{ex:intro:pseudopartitive}
%  \begin{xlist}
    \ex[ ]{\label{ex:intro:pseudopartitive1}\gll Wir trinken [[eine Tasse]\Sub{Acc} [eines leckeren Kaffees]\Sub{Gen}]\Sub{Acc}.\\
    we drink a cup a tasty coffee\\
    \glt We drink a cup of a tasty coffee.}
%    \ex[*]{\label{ex:intro:pseudopartitive2} Wir trinken [[eine Tasse]\Sub{Acc} [einen leckeren Kaffee]\Sub{Acc}]\Sub{Acc}.}
%  \end{xlist}
\end{exe}

If the kind noun is bare -- \ie\ if it does neither come with a determiner nor a modifying adjective -- it has to agree in case with the measure noun, and the genitive seen in the PGC is not acceptable, see (\ref{ex:intro:narrowapposition2}).

\begin{exe}
%  \ex\label{ex:intro:narrowapposition}
%  \begin{xlist}
%    \ex[*]{\label{ex:intro:narrowapposition1} Wir trinken [[eine Tasse]\Sub{Acc} [Kaffees]\Sub{Gen}]\Sub{Acc}.}
    \ex[ ]{\label{ex:intro:narrowapposition2}\gll Wir trinken [[eine Tasse]\Sub{Acc} [Kaffee]\Sub{Acc}]\Sub{Acc}.\\
    we drink a cup coffee\\
    \glt We drink a cup of coffee.}
%  \end{xlist}
\end{exe}

This construction is usually classified as a \textit{Narrow Apposition Construction} \citep{Loebel1986}, henceforth NAC.%
\footnote{The construction as in (\ref{ex:intro:narrowapposition2}) is also referred to as the \textit{Direct Partitive Construction} for other Germanic languages in which the PGC with the synthetic genitive is not available.
This nomenclature makes sense in contrast to the \textit{Indirect Partitive Construction} with prepositional linkers translating to `of' -- \ie\ analytic genitives -- in such languages, see \cite{HankamerMikkelsen2008} for Danish.
For German, this terminology is not distinctive enough, which is why I use the terms NAC and PGC.}
Notice that the unavailability of the genitive on the kind noun can be seen as following from a rather quirky constraint that genitive NPs in German require the presence of some strongly case-marked element (determiner or adjective) in addition to the head noun in order to be acceptable \citep{GallmannLindauer1994,Schachtl1989}.
While only an accusative is shown in (\ref{ex:intro:narrowapposition2}), the kind noun obligatory agrees in case also with nominative and dative measure nouns.

@@

First of all, (\ref{it:intro:idiot}) refers to claims found in some grammars that a generic nominative, accusative, and even dative on the kind noun are used instead of the genitive (\PGCa) or case agreement (\NACa).
Overviews can be found in \citealp{Hentschel1993,Zimmer2015}.
It was shown empirically in \cite{Hentschel1993} that such variants are de facto not acceptable.
Also, in my corpus sample, they simply did not occur.
Even if they are accepted by some speakers, their extremely low frequency makes it virtually impossible to study them using either corpus methods (Section~\ref{sec:corpusstudies}), and I consequently ignore them.

@@

Turning to (\ref{it:intro:plurl}), readers might have noticed that so far only MNPs denoting quantities of substances (mass kind nouns such as \textit{ein Glas roter Wein\slash roten Weines} `a glass of red wine') have been discussed.
If the kind noun is a plural count noun as in \textit{ein Sack kleine Äpfel} (\NACa) or \textit{ein Sack kleiner Äpfel} (\PGCa) `a bag of small apples', a similar alternation between PGC and NAC can be observed.
In line with experimental results reported in \citet[15--16]{Zimmer2015}, I found that the PGC is so dominant with plural kind nouns (67 of 861 cases or over 92\%, cf.\ Section~\ref{sec:corpusstudies}) that the alternation cannot be analysed in the same way as in the singular case.%
\footnote{More concretely, if these cases were included in the regression analysis of the corpus data along with a factor encoding the number of the kind noun, this factor would most assuredly override any other regressor for the data points with a plural kind noun.}
While this will play a role in the interpretation of the corpus findings, MNPs with plural kind nouns will not be included in the corpus study and the experiments reported here.

@@

Second, constructions with \textit{voll} (\textit{von})\slash\textit{voller} `full (of)' and \textit{mit} `with' are available, see (\ref{ex:alternatives}).

@@

My analysis is based on the idea that the relevant syntactic structure [N\Sub{1}~[A~N\Sub{2}]\Sub{NP\Sub{2}}]\Sub{NP\Sub{1}} as instantiated in the \NACa\ and the \PGCa\ is ambiguous.
To show this, the first question is which noun constitutes the head of the whole construction.
This was answered quite clearly by \cite{Loebel1986} already (see also \citealp[213]{Eschenbach1994}, and \citealp[16]{GallmannLindauer1994}).
Subject-verb agreement is always realised on the measure noun, and we can therefore assume that the measure noun is the head.
However, the MNP-internal structure has more interesting cues to offer if the strong\slash weak inflection patterns of adjectives are taken into account.
In NPs with a strongly inflected determiner, attributive adjectives inflect according to the massively syncretistic \textit{weak} pattern.
%\footnote{The weak pattern has only two suffixes.
%The structural cases (nominative and accusative) in the singular are marked with \textit{-e}, the oblique cases (dative and genitive) as well as the entire plural are marked with \textit{-en}.
%The only exception to this rule is the masculine accusative singular, which is also marked with \textit{-en}.}
If there is no determiner (as is the case in the alternating constructions), attributive adjectives inflect like determiners themselves, however.
This is called the \textit{strong} inflectional pattern.
Thus, the adjectives in the \NACa\ and the \PGCa\ have properties of adjectives as well as determiners.
On the one hand, they are lexical adjectives and function as attributive modifiers.
On the other hand, they are inflected like determiners, and they are the leftmost element in the NP, which is typical of determiners.
This unusual double nature of adjectives in NPs without determiners leads to a plausible probabilistic interpretation of the pattern shown in Table~\ref{tab:constructions}.
Whenever speakers classify the adjective in the kind noun phrase more as a determiner, they have to use the \PGCa\ because, if there is a determiner, the PGC is the only option.
When they classify the adjective more as an adjective, the kind NP has no determiner, and they have to use the \NACa.%
\footnote{While the generative analysis presented in \cite{Bhatt1990} cannot properly deal with probabilistic effects, Bhatt comes close to this interpretation by analysing the kind NP in the GPC as a DP and in the NAC as an NP.}

This morpho-syntactic ambiguity means that the \NACa\ is in fact a \NACb\ in disguise, and the \PGCa\ is a \PGCd\ in disguise.
This should ideally be reflected in the following basic selection effect:
It is known from frameworks like Collexeme Analysis \citep{GriesStefanowitsch2004} that lemmas are attracted with different strengths by competing constructions.
If the \NACa\ is highly similar to the \NACb\ and the \PGCa\ is highly similar to the \PGCd, the probability with which individual noun lemmas appear in the alternating constructions should be predictable at least partly from the relative frequency with which the same lemmas are used in the non-alternating constructions (see \citealp[246--249]{Levshina2016} for a similar idea in a different context).
Nouns which occur proportionally more often in the \PGCd\ should favour the \PGCa, and nouns which occur proportionally more often in the \NACb\ should favour the \NACa.
This basic attraction effect will be quantified in the corpus study Section~\ref{sec:corpusstudies}.

@@

Conversely, the NAC completely lacks this ability to form true partitives, and it thus forms the more prototypical environment for expressing measurement (as opposed to partitivity).

@@

As described above, the grammaticalisation path leads from NPs denoting individuated objects standing in a \textit{part-of} relation to a construction with a more diffuse \textit{quantity-of} relation.
Both types of relations can be numerically quantified -- in as much as a precise number of \textit{parts} or a numerically exact \textit{quantity} can be specified --, but it is much more prototypical of quantities to be specified with numerical precision.
Since the \NACa\ is more closely associated with the \textit{quantity-of} relation, cardinals as attributes of the measure noun are expected to have a higher proportional frequency in the \NACa.
For illustration, (\ref{ex:determiners}) shows the expected variants under this hypothesis.
In (\ref{ex:determiners:nac}), the measure noun is modified by a cardinal \textit{drei} `three', and hence the \NACa\ is preferred.
In (\ref{ex:determiners:pgc}), the measure noun is modified by a non-cardinal determiner \textit{einige} `some', and the \PGCa\ is preferred.

@@

The statistical model presented in Section~\ref{sec:corpusstudies} will be specified in a way that it can detect such a preference.

Finally, it was found that the \PGCa\ is more typical of higher registers or even exclusive to written language (see \citealp[320--323]{Hentschel1993}).
This is not surprising in as much as the genitive -- an intrinsic part of the PGC -- is generally underrepresented in colloquial vernacular variants of German as a result of a diachronic process wherein many (but by no means all) uses of the genitive are replaced by other cases or periphrastic constructions \citep{FleischerSchallert2011}.
Under an integral view of prototypes, which incorporate effects related to larger contexts and registers, such preferences can be to be part of the construction prototypes.
In the corpus study in Section~\ref{sec:corpusstudies}, register effects will therefore be modeled -- even if only using two very simple proxy variables.
